
\section{Executive Summary}

\subsection{Introduction}

Life Hack Innovations and Cable \& Wireless Worldwide have entered into an agreement for the delivery of a Maestro™ Smart Building Project to a subset of C\&WW’s real estate portfolio. The agreement leverages Elutions’ technology and subject matter expertise to maximize the economic and operational benefit of the Maestro™ Smart Building Solution to assist C\&WW in achieving significantly reduced energy spend as well as reinforce their desire to:
\begin{itemize}
  \item 	Lower facility operating costs through the efficient and effective use of energy resources
  \item 	Improve productivity by maximizing return on assets deployed
  \item 	Address Corporate Responsibility by lowering CO2 emissions and carbon impact on an enterprise scale
\end{itemize}

The Maestro™ Smart Building initiative is the cornerstone of development in next-generation global energy conservation measures. The key focus of this initiative is the quantifiable delivery of substantial and sustainable cost reduction in both Opex and Capex achieved through the deployment of next-generation intelligent building performance management hardware, software and control analytics and replacing reliance on ASHRAE and compliance audits with continuous commissioning.

Another key deliverable through the Maestro™ Smart Building initiative is the introduction of automated utilities invoice verification and share of related gains. This is achieved through the bill reconciliation, tariff management and contract optimization capabilities within the Maestro™ Smart Building platform. The key deliverables here will be:

\begin{itemize}
  \item 	Accurate a verifiable utility bills on a global basis
  \item	Intelligent energy purchase based on known demand profiles on a facility, region or country basis
  \item Tariff and Contract optimization through peak demand management
  \end{itemize}
  
  
\subsection{Scope}

45 C\&WW sites were selected as the showcase deployment of the Maestro™ Smart Building technology. The deployment was broken out into two tranches of 10 and 35 sites; respectively, the deployment of the first 10 sites commenced in July of 2012 while the 35 sites commenced in January of 2013.  The First Tranche sites were identified as excellent candidates to demonstrate the potential for the Maestro™ Smart Building technology within the Cable \& Wireless’ estate because of their large energy consumption profiles and the immediate opportunity for control automation and advanced analytics to be implemented. The Second Tranche sites were released based off of the performance of the technology platform in the First Tranche. The 35 sites contain more than 5 Datacenters and more than 20 Network Operating facilities where the savings opportunities could exceed the savings achieved in the First Tranche. 
This document provides the details behind the proposed approach, observations and recommendations that substantiate the estimated energy and cost reduction that will be realized.


\subsection{Overview}

Over the next two months, Life Hack Innovations, Inc. will continue to conduct extensive site audits within C\&WW’s facility portfolio to establish the scope and scale of the opportunity to reduce energy consumption. The site audits will also be used to determine the required infrastructure architecture to support the energy reduction.

\subsection{Executive Summary–-Key Notes}

\begin{itemize}
  \item •	The net benefit result from this deployment, based on validated findings from existing Tier 1 clients and from utility information provided by Cable \& Wireless, is expected to yield over £24.5M in savings across 5 years.
  \item •	Benefits identified as part of the Maestro™ Smart Building implementation include:
  \begin{enumerate}[-]
   \item 	Energy consumption and cost reduction
   \item 	Maintenance cost reductions
   \item 	Increased Return on Investments
   \item 	Informed investment decision making
   \item 	Implementation, maintenance and enforcement of Corporate Standards consistently across the entire estate
   \item 	Establish transparency and governance around demand of building user/business versus C\&WW Corporate Sustainability Plan
  \end{enumerate}
\end{itemize}
\begin{itemize}
  \item 	Quantifiable benefits include:
  \begin{enumerate}[-]
     \item 	Energy savings 
     \item 	Extension of HVAC asset life
     \item 	Asset maintenance cost reductions primarily due to optimized runtime
      
     
   \end{enumerate}
\end{itemize}